Wrinkling and yielding of protein gel

### 2013-09-10 poster_Rome.tex
Scale bars

	\begin{tikzpicture}[inner sep=0, very thick]
	\node[anchor=west] (a) {\includegraphics{cas3p2_fluo0p8_GDL4_50um_coating_2_zoom2}};
	\node at (3.5\TPHorizModule,0) (b) {\includegraphics{cas3p2_fluo0p8_GDL4_50um_coating_2_zoom6}};
	\node[anchor=east] at (7\TPHorizModule,0) (c) {\includegraphics[height=65mm]{cas3p2_fluo0p8_GDL4_50um_coating_2_transmission}};
	\draw[Accent2] (a.north west) ++(36.4mm, -25mm) rectangle +(28.9mm,-21.7mm) -- (b.south west) (a.north west) ++(65.3mm, -25mm) -- (b.north west);
	\draw[Main] (b.north west) ++(34mm,-34mm) rectangle +(27mm,-19.7mm) -- (c.south west) (b.north west) ++(61mm,-34mm) --(c.north west);
	\draw[Accent1] (c.south west) ++(29mm,29mm) rectangle +(36mm,36mm);
	%\includegraphics{cas3p2_fluo0p8_GDL4_50um_coating_2_zoom6}
	%\includegraphics[height=65mm]{cas3p2_fluo0p8_GDL4_50um_coating_2_transmission}
	\end{tikzpicture}

@@

\begin{textblock}{15}(0,8)
	\Head{Pattern kinetics by transmission macroscope}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}ccccccc}
	33 min & 38 min & 43 min & 48 min & 1h & 1h15 & 2h30\\
	\includegraphics[width=2\TPHorizModule]{prise_0100_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0130_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0160_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0190_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0250_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0360_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0799_resized.jpg}\\
	\end{tabular*}
\end{textblock}

@@

	\includegraphics[width=\textwidth]{collage_cut}

	Tilled, enhanced relief
\end{textblock}

@@

\begin{textblock}{15}(0,14)
	\Head{Wrinkling kinetics by confocal microscope}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}ccccccc}
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t047_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t056_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t065_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t074_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t092_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t125_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t260_crop_resized.jpg}\\
\end{tabular*}
\end{textblock}

\begin{textblock}{4}(0,16)
	\Head{Composition}
	\Subhead{Less gdl}
	\begin{itemize}
		\item slower kinetics
		\item stronger gel
		\item weaker overshoot
		\item same fundamental \linebreak wavelength
		\item less harmonics
	\end{itemize}
	\Subhead{More gdl}
	\begin{itemize}
		\item plasticity
	\end{itemize}
\end{textblock}
\begin{textblock}{2}(2,16)
	\addvspace{4.4em}
	\hfill bottom surface, \textsc{gdl} 5\%\\
	\includegraphics[width=2\TPHorizModule]{plastic_confocal}
\end{textblock}

@@

	\begin{tikzpicture}
	\begin{loglogaxis}[%
		name=a,
		xlabel={$t\,(s)$},
		ylabel={Shear rate $(s^{-1})$},
		]
		\addplot+[no marks, Accent2] file {Y34_strain_rate_log.txt};
		\draw[<->] (axis cs:1e-1,1) -- (axis cs:1.3e3,5e-4) node[midway,above,rotate=-21] {Andrade};
		\node at (axis cs:1.3e3,1e-4) (det){};
		\node at (axis cs:2.3e3,1e4) (touch){};
	\end{loglogaxis}
	\draw[<-, Accent1, ultra thick] (det) -- ++(0,-4em) node[left] {Fractures appear};
	\draw[<-, Accent1, ultra thick] (touch) -- ++(0,3em) node[left] {Fractures meet};
	\end{tikzpicture}\hfill
	\begin{tikzpicture}[inner sep=0]
		\node[above right] at (0,1em) {\includegraphics[width=1.5\TPHorizModule, trim=0 6mm 2cm 1cm,clip=true]{Y210_SSC300_avant_div.jpg}};
		\node[below right] (b){\includegraphics[width=1.5\TPHorizModule, trim=0 6mm 2cm 1cm,clip=true]{Y210_SSC300_premiere_frac.jpg}};
		\node[below left=0 of b.north east]{\includegraphics[width=0.75\TPHorizModule]{detail_premiere_frac.jpg}};
		\draw[Accent2,radius=0.07\TPHorizModule] ++(b.north east) +(-1.14\TPHorizModule,-1.05\TPHorizModule) circle;
		\draw[Accent2,radius=0.09\TPHorizModule] ++(b.north east) +(-0.435\TPHorizModule,-0.375\TPHorizModule) circle;
	\end{tikzpicture}

>>>>

	\begin{tikzpicture}[inner sep=0, very thick]
	\node[anchor=west] (a) {\includegraphics{cas3p2_fluo0p8_GDL4_50um_coating_2_zoom2}};
	\node at (3.5\TPHorizModule,0) (b) {\includegraphics{cas3p2_fluo0p8_GDL4_50um_coating_2_zoom6}};
	\node[anchor=east] at (7\TPHorizModule,0) (c) {\includegraphics[height=65mm]{cas3p2_fluo0p8_GDL4_50um_coating_2_transmission}};
	\draw[Accent2] (a.north west) ++(36.4mm, -25mm) rectangle +(28.9mm,-21.7mm) -- (b.south west) (a.north west) ++(65.3mm, -25mm) -- (b.north west);
	\draw[Main] (b.north west) ++(34mm,-34mm) rectangle +(27mm,-19.7mm) -- (c.south west) (b.north west) ++(61mm,-34mm) --(c.north west);
	\draw[Accent1] (c.south west) ++(29mm,29mm) rectangle +(36mm,36mm);
	\draw[ultra thick] (a.south west) ++(0,-0.25em) -- ++(30.588mm,0) node[pos=0.5, below=0.25em, font=\small] {\SI{1}{\centi\metre}};
	\draw[ultra thick] (b.south west) ++(0,-0.25em) -- ++(45.774mm,0) node[pos=0.5, below=0.25em, font=\small] {\SI{5}{\milli\metre}};
	\draw[ultra thick] (c.south west) ++(0,-0.25em) -- ++(30.415mm,0) node[pos=0.5, below=0.25em, font=\small] {\SI{1}{\milli\metre}};
	\end{tikzpicture}

@@

\begin{textblock}{15}(0,8)
	\Head{Pattern kinetics by transmission macroscope}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}p{2\TPHorizModule}llllll}
	33 min\hfill \begin{tikzpicture}[inner sep=0]
		\draw[ultra thick] (0,0) -- ++(0.355\TPHorizModule,0) node[pos=0.5, above=0, font=\small] {\SI{1}{\centi\metre}};
	\end{tikzpicture}&
	 38 min & 43 min & 48 min & 1h & 1h15 & 2h30\\
	\includegraphics[width=2\TPHorizModule]{prise_0100_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0130_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0160_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0190_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0250_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0360_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{prise_0799_resized.jpg}\\
	\end{tabular*}
\end{textblock}

@@

	\begin{tikzpicture}[inner sep=0]
		\node[above right]{\includegraphics[width=\textwidth]{collage_cut}};
		\draw[ultra thick] ++(0,0.5em) -- ++(0.33\textwidth,0) node[pos=0.5, below=0.25em, font=\small] {\SI{1}{\milli\metre}};
	\end{tikzpicture}\\
	Tilled, enhanced relief
\end{textblock}

@@

\begin{textblock}{15}(0,14)
	\Head{Wrinkling kinetics by confocal microscope}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lllllll}
	\raisebox{-0.75em}{\begin{tikzpicture}[inner sep=0]
		\node[above right]{\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t047_crop_resized.jpg}};
		\draw[ultra thick] ++(0,0.02\TPHorizModule) -- ++(1.55\TPHorizModule,0) node[pos=0.5, below=0.25em, font=\small] {\SI{1}{\milli\metre}};
	\end{tikzpicture}}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t056_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t065_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t074_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t092_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t125_crop_resized.jpg}&
	\includegraphics[width=2\TPHorizModule]{cas3p2_fluo0p8_GDL4_2_t260_crop_resized.jpg}\\
\end{tabular*}
\end{textblock}

\begin{textblock}{4}(0,16)
	\Head{Composition}
	\Subhead{Less gdl}
	\begin{itemize}
		\item slower kinetics
		\item stronger gel
		\item weaker overshoot
		\item same fundamental \linebreak wavelength
		\item less harmonics
	\end{itemize}
	\Subhead{More gdl}
	\begin{itemize}
		\item plasticity
	\end{itemize}
\end{textblock}
\begin{textblock}{2}(2,16)
	\addvspace{2.4em}
	bottom surface, \textsc{gdl} 5\%\\
	\begin{tikzpicture}[inner sep=0]
		\draw[ultra thick] (0,0) -- ++(1.11\TPHorizModule,0) node[pos=0.5, above=0, font=\small] {\SI{500}{\micro\metre}};
	\end{tikzpicture}

	\includegraphics[width=2\TPHorizModule]{plastic_confocal}
\end{textblock}

@@

	\begin{tikzpicture}
	\begin{loglogaxis}[%
		name=a,
		xlabel={$t\,(s)$},
		ylabel={Shear rate $(s^{-1})$},
		]
		\addplot+[no marks, Accent2] file {Y34_strain_rate_log.txt};
		\draw[<->] (axis cs:1e-1,1) -- (axis cs:1.3e3,5e-4) node[midway,above,rotate=-21] {Andrade};
		\node at (axis cs:1.3e3,1e-4) (det){};
		\node at (axis cs:2.3e3,1e4) (touch){};
	\end{loglogaxis}
	\draw[<-, Accent1, ultra thick] (det) -- ++(0,-4em) node[left] {Fractures appear};
	\draw[<-, Accent1, ultra thick] (touch) -- ++(0,3em) node[left] {Fractures meet};
	\end{tikzpicture}\hfill
	\begin{tikzpicture}[inner sep=0]
		\node[above right] at (0,1em) {\includegraphics[width=1.5\TPHorizModule, trim=0 6mm 2cm 1cm,clip=true]{Y210_SSC300_avant_div.jpg}};
		\node[below right] (b){\includegraphics[width=1.5\TPHorizModule, trim=0 6mm 2cm 1cm,clip=true]{Y210_SSC300_premiere_frac.jpg}};
		\node[below left=0 of b.north east]{\includegraphics[width=0.75\TPHorizModule]{detail_premiere_frac.jpg}};
		\draw[Accent2,radius=0.07\TPHorizModule] ++(b.north east) +(-1.14\TPHorizModule,-1.05\TPHorizModule) circle;
		\draw[Accent2,radius=0.09\TPHorizModule] ++(b.north east) +(-0.435\TPHorizModule,-0.375\TPHorizModule) circle;
		\draw[ultra thick] (a.south west) ++(0,0.25em) -- ++(0.5\TPHorizModule,0) node[pos=0.5, above=0, font=\small] {\SI{2}{\centi\metre}};
	\end{tikzpicture}
